\thetitle

### 2022-03-29 paper/paper.tex
benchmarks, performance

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. (Alternatively, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.) Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `대학 지원 포트폴리오 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. (예산 제약 조건은 또한 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수도 있다.) 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최대값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다.
\fi

% This problem is not exclusively of theoretical interest. Companies sell products ...

\ifen
As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.
\else
Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 포트폴리오 최적화 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Chao는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

\ifen
The integer formulation of the college application problem can also be viewed as a kind of binary knapsack problem with a polynomial objective function of degree $m$. Our branch-and-bound and dynamic programming algorithms closely resemble existing algorithms for knapsack problems (Martello and Toth 1990, \S\,2.5--6). In fact, by manipulating the admissions probabilities, the objective function can be made to approximate a linear function of the characteristic vector to an arbitrary degree of accuracy, a fact that we exploit in our NP-completeness proof. Previous research has introduced various forms of stochasticity to the knapsack problem, including variants in which each item's utility takes a known probability distribution (Steinberg and Parks 1979; Carraway et al. 1993) and an online context in which the weight of each item is observed after insertion into the knapsack (Dean et al. 2008). Our problem superficially resembles the preference-order knapsack problem considered by Steinberg and Parks and Carraway et al., but these models lack the college application problem's unique ``maximax'' form. Additionally, unlike those models, we do not attempt to replace the real-valued objective function with a preference order over \emph{outcome distributions,} which introduces technical issues concerning competing notions of stochastic dominance (Sniedovich 1980). We take for granted the student's preferences over \emph{outcomes} (as encoded in the $t_j$-values), and are interested instead in an efficient computational approach to the well-defined problem above.
\else
대학 지원 문제의 정수 모형은 $m$차 다항식을 목적함수로 갖춘 일종의 이진 배낭 문제로 볼 수도 있다. 본 논문에서 제시하는 분지한계법과 동적 계획 해법은 배낭 문제를 위한 기존 알고리즘과 매우 비슷하다 (Martello와 Toth 1990, \S\,2.5--6). 입학 확률을 적당히 조정하면 특성벡터의 선형 함수를 원래 목적함수로 원하는 만큼의 정확성을 가지고 근사할 수 있으며 NP-completeness 증명에서 이 성질을 활용한다. 배낭 문제에 확률성을 도입한 선행 연구 중, 각 상품의 효용이 정해진 확률 분포로 결정되는 모형(Steinberg와 Parks 1979; Carraway 외 1993), 그리고 배낭에 삽입한 다음에 상품의 무게를 관측할 수 있는 온라인 모형 (Dean 외 2008) 등이 있다. 본 연구가 고려하는 문제는 Steinberg와 Parks 그리고 Carraway 외가 고려한 ``우선순위 배낭 문제''와는 유사성을 가지지만, 우선순위 배낭 문제는 대학 지원 문제의 특색인 `maximax' 형태를 가지지는 않는다. 또한 우선순위 모형과 달리, 본 연구에서 실수값 목적함수를 선호 순위를 정의해야 하는 `결과 분포'로 대체할 필요가 없다. 확률적 우위에 대한 상반된 개념들의 문제를 야기시키기 때문이다 (Sniedovich 1980). 대신 $t_j$-값으로 유도된 학생의 `결과'에 대한 선호 순위를 받아들여 위에서 정의한 것처럼 명확히 정의된 문제를 위한 효율적인 계산법을 지향한다.
\fi

\ifen
We take special interest in the validity of greedy optimization algorithms for the set function $v(\mathcal{X})$, such as the algorithm that iteratively adds the school that elicits the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges reward students who tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the optimal portfolio.
\else
본 연구에서 특히 탐욕 해법의 가능성에 관심을 기울인다. 예를 들어 예산이 다 소비될 때까지 목적함수를 가장 많이 증가시키는 학교를 차례대로 추가하는 알고리즘은 일종의 탐욕 해법이다. 탐욕 해법은 예산 $H$으로 모수화된 해의 순서를 유도하며 그의 원소들은 `포함 사슬 관계'(nestedness)로 연결한다. 즉 $H \leq H'$일 때, 예산 $H$에 해당하는 탐욕 해는 예산 $H'$에 해당하는 탐욕 해의 부분집합이 된다. Rozanov와 Tamir (2020)가 주장하듯, 최적해가 포함 사슬 관계를 가지면 최적해를 구하는 것뿐 아니라 정보가 불확실한 상황에서 최적해를 구현하는 데에도 유용하다. 가령, 많은 미국 대학의 지원 기한은 11월 초인데 학업 계획서를 학교의 취향에 맞춰서 작성해야 하므로 여름부터 원서를 작성하는 학생이 많다. 그러나 지원 예산은 10월 말까지 모를 수도 있다. 포함 사슬 관계, 또는 탐욕 해법의 타당성은 완전한 예산 정보가 없어도 학교가 최적 포트폴리오에 진입하는 순서대로 원서를 작성하면 최적 전략을 구현해 낼 수 있음을 의미한다.
\fi

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offers any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 하위 모듈 집합 함수(submodular set function)를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 알고리즘 등 3가지 해법을 제안한다. 
\fi

@@

\begin{proof}
\ifen It is obvious that the problem is in NP.
\else 문제가 NP에 속하는 것은 명백하다.\fi

@@

\ifen
The algorithm is initialized by populating $\mathfrak{T}$ with the root node $n_0 = (\O, \O, \mathcal{C})$. At each iteration, it selects the node $n \in \mathfrak{T}$ having the highest $v_{\mathrm{LP}}^*[n]$-value, generates its children, and removes $n$ from the candidate set. Next, the children $n'$ of $n$ are inspected; if one of them yields a new optimal solution, then we mark it as the best candidate and fathom any nodes $n''$ for which  $v_{\mathcal{I}}[n'] >  v_{\mathrm{LP}}^*[n'']$. When no nodes remain in the candidate set, the algorithm has explored every branch, so it returns the best candidate and terminates.
\else
$\mathfrak{T}$에 뿌리 마디 $n_0 = (\O, \O, \mathcal{C})$를 넣어서 알고리즘을 초기화한다. 각 반복단계에서 $v_{\mathrm{LP}}^*[n]$-값이 가장 높은 마디 $n \in \mathfrak{T}$을 선택한다. $n$의 새끼를 생성하고 후보 집합에서 제거한다. 그다음에 $n$의 각 새끼 마디 $n'$을 검증한다. 그중에 새로운 최적해를 발견하면 이를 가장 좋은 후보로 표하고  $v_{\mathcal{I}}[n'] >  v_{\mathrm{LP}}^*[n'']$인 마디 $n''$을 후보 집합에서 제거한다. 후보 집합이 공집합이 되면 알고리즘이 모든 가지를 탐색했으므로 가장 좋은 후보를 출력하고 종료한다.
\fi

@@

\ifen \subsection{Pseudopolynomial-time dynamic program} \else\subsection{의사 다항 시간 동적 계획} \fi
\ifen
In this subsection, we assume, with a small loss of generality, that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$, and provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$-time. The algorithm resembles a familiar dynamic programming algorithm for the binary knapsack problem (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Garey and Johnson 1979, \S\,4.2).
\else
본 절에서 일반성을 약간 제한해서 $g_j \in \mathbb{N}$ for $j = 1\dots m$과 $H \in\mathbb{N}$임을 가정한다. 이때 엘리스의 문제를 위한 $O(Hm + m\log m)$-시간 해법을 제시한다. 해법은 이진 배낭 문제를 위한 익숙한 동적 계획 해법과 비슷하다 (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). 알마의 문제와 달리, 여기에서 $H \leq m$임을 가정할 수 없으므로 이는 의사 다항 시간 해법이라고 한다 (Garey and Johnson 1979, \S\,4.2).
\fi

@@

@@

>>>>

\ifen
We interpret this problem as the \emph{optimal college application} problem, as follows. Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. (Alternatively, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.) Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. (The problem is also conformable to other competitive matching games such as job application.)
\else
다음 해석에 따라 이를 `대학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. (예산 제약 조건은 또한 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수도 있다.) 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최대값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다. (취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위에 문제를 적용할 수 있다.)
\fi

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize students' application strategy.  To the extent that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 비율은 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정되는 만큼, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

\ifen
From a methodological standpoint, as Chao (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Chao는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

\ifen
The integer formulation of the college application problem can also be viewed as a kind of binary knapsack problem with a polynomial objective function of degree $m$. Our branch-and-bound and dynamic programming algorithms closely resemble existing algorithms for knapsack problems (Martello and Toth 1990, \S\,2.5--6). In fact, by manipulating the admissions probabilities, the objective function can be made to approximate a linear function of the characteristic vector to an arbitrary degree of accuracy, a fact that we exploit in our NP-completeness proof. Previous research has introduced various forms of stochasticity to the knapsack problem, including variants in which each item's utility takes a known probability distribution (Steinberg and Parks 1979; Carraway et al. 1993) and an online context in which the weight of each item is observed after insertion into the knapsack (Dean et al. 2008). Our problem superficially resembles the preference-order knapsack problem considered by Steinberg and Parks and Carraway et al., but these models lack the college application problem's singular ``maximax'' form. Additionally, unlike those models, we do not attempt to replace the real-valued objective function with a preference order over \emph{outcome distributions,} which introduces technical issues concerning competing notions of stochastic dominance (Sniedovich 1980). We take for granted the student's preferences over \emph{outcomes} (as encoded in the $t_j$-values), and focus instead on an efficient computational approach to the well-defined problem above.
\else
대학 지원 문제의 정수 모형은 $m$차 다항식을 목적함수로 갖춘 일종의 이진 배낭 문제로 볼 수도 있다. 본 논문에서 제시하는 분지한계법과 동적 계획 해법은 배낭 문제를 위한 기존 알고리즘과 매우 비슷하다 (Martello와 Toth 1990, \S\,2.5--6). 입학 확률을 적당히 조정하면 특성벡터의 선형 함수를 원래 목적함수로 원하는 만큼의 정확성을 가지고 근사할 수 있으며 NP-completeness 증명에서 이 성질을 활용한다. 배낭 문제에 확률성을 도입한 선행 연구 중, 각 상품의 효용이 정해진 확률 분포로 결정되는 모형(Steinberg와 Parks 1979; Carraway 외 1993), 그리고 배낭에 삽입한 다음에 상품의 무게를 관측할 수 있는 온라인 모형 (Dean 외 2008) 등이 있다. 본 연구가 고려하는 문제는 Steinberg와 Parks 그리고 Carraway 외가 고려한 ``우선순위 배낭 문제''와는 유사성을 가지지만, 우선순위 배낭 문제는 대학 지원 문제의 특색인 `maximax' 형태를 가지지는 않는다. 또한 우선순위 모형과 달리, 본 연구에서 실수값 목적함수를 선호 순위를 정의해야 하는 `결과 분포'로 대체할 필요가 없다. 확률적 우위에 대한 상반된 개념들의 문제를 야기시키기 때문이다 (Sniedovich 1980). 대신 $t_j$-값으로 유도된 학생의 `결과'에 대한 선호 순위를 받아들여 위에서 정의한 것처럼 명확히 정의된 문제를 위한 효율적인 계산법을 지향한다.
\fi

\ifen
We take special interest in the validity of greedy optimization algorithms for the set function $v(\mathcal{X})$, such as the algorithm that iteratively adds the school that elicits the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges reward students who tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the optimal portfolio.
\else
본 연구에서 특히 탐욕 해법의 가능성에 관심을 기울인다. 예를 들어 예산이 다 소비될 때까지 목적함수를 가장 많이 증가시키는 학교를 차례대로 추가하는 알고리즘은 일종의 탐욕 해법이다. 탐욕 해법은 예산 $H$로 모수화된 해의 순서를 유도하며 그의 원소들은 `포함 사슬 관계'(nestedness)로 연결된다. 즉 $H \leq H'$일 때, 예산 $H$에 해당하는 탐욕 해는 예산 $H'$에 해당하는 탐욕 해의 부분집합이 된다. Rozanov와 Tamir (2020)가 주장하듯, 최적해가 포함 사슬 관계를 가지면 최적해를 구하는 것뿐 아니라 정보가 불확실한 상황에서 최적해를 구현하는 데에도 유용하다. 가령, 많은 미국 대학의 지원 기한은 11월 초인데 학업 계획서를 학교의 취향에 맞춰서 작성해야 하므로 여름부터 원서를 작성하는 학생이 많다. 그러나 지원 예산은 10월 말까지 모를 수도 있다. 포함 사슬 관계, 또는 탐욕 해법의 타당성은 완전한 예산 정보가 없어도 학교가 최적 포트폴리오에 진입하는 순서대로 원서를 작성하면 최적 전략을 구현해 낼 수 있음을 의미한다.
\fi

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 하위 모듈 집합 함수(submodular set function)를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 알고리즘 등 3가지 해법을 제안한다. 
\fi

@@

\begin{proof}
\ifen It is obvious that the problem is in NP.
\else 문제가 NP에 속하는 것은 자명하다.\fi

@@

\ifen
The algorithm is initialized by populating $\mathfrak{T}$ with the root node $n_0 = (\O, \O, \mathcal{C})$. At each iteration, it selects the node $n \in \mathfrak{T}$ having the highest $v_{\mathrm{LP}}^*[n]$-value, generates its children, and removes $n$ from the candidate set. Next, the children $n'$ of $n$ are inspected and added to the tree. If one of the children yields a new optimal solution, then we mark it as the best candidate and fathom any nodes $n''$ for which  $v_{\mathcal{I}}[n'] >  v_{\mathrm{LP}}^*[n'']$. When no nodes remain in the candidate set, the algorithm has explored every branch, so it returns the best candidate and terminates.
\else
$\mathfrak{T}$에 뿌리 마디 $n_0 = (\O, \O, \mathcal{C})$를 넣어서 알고리즘을 초기화한다. 각 반복단계에서 $v_{\mathrm{LP}}^*[n]$-값이 가장 높은 마디 $n \in \mathfrak{T}$을 선택한다. $n$의 새끼를 생성하고 후보 집합에서 제거한다. 그다음에 $n$의 각 새끼 마디 $n'$을 검증하고 나무에 추가한다. 새끼 마디 중에 새로운 최적해를 발견하면 이를 가장 좋은 후보로 표하고  $v_{\mathcal{I}}[n'] >  v_{\mathrm{LP}}^*[n'']$인 마디 $n''$을 후보 집합에서 제거한다. 후보 집합이 공집합이 되면 알고리즘이 모든 가지를 탐색했으므로 가장 좋은 후보를 출력하고 종료한다.
\fi

@@

\ifen \subsection{Pseudopolynomial-time dynamic program} \else\subsection{의사 다항 시간 동적 계획} \fi
\ifen
In this subsection, we assume, with a small loss of generality, that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$, and provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$-time. The algorithm resembles a familiar dynamic programming algorithm for the binary knapsack problem (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Garey and Johnson 1979, \S\,4.2). However, it is quite effective for typical college-application instances in which the application costs are small integers.
\else
본 절에서 일반성을 약간 제한해서 $g_j \in \mathbb{N}$ for $j = 1\dots m$과 $H \in\mathbb{N}$임을 가정한다. 이때 엘리스의 문제를 위한 $O(Hm + m\log m)$-시간 해법을 제시한다. 해법은 이진 배낭 문제를 위한 익숙한 동적 계획 해법과 비슷하다 (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). 알마의 문제와 달리, 여기에서 $H \leq m$임을 가정할 수 없으므로 이는 의사 다항 시간 해법이라고 한다 (Garey and Johnson 1979, \S\,4.2). 그러나 지원 비용이 작은 정수가 되는 전형적인 대학 지원 문제 인스턴스에 대해 매우 효율적인 해법이다.
\fi

@@

Acharya, Mohan S., Asfia Armaan, and Aneeta S. Antony. 2019. ``A Comparison of Regression Models for Prediction of Graduate Admissions.'' In \emph{Second International Conference on Computational Intelligence in Data Science.} \url{https://doi.org/10.1109/ICCIDS.2019.8862140}.

@@

Sklarow, Mark. 2018. \emph{State of the Profession 2018: The 10 Trends Reshaping Independent Educational Consulting.} Technical report, Independent Eduational Consultants Association. \url{https://www.iecaonline.com/wp-content/uploads/2020/02/IECA-Current-Trends-2018.pdf}.
